---
title: "Final_Quantitative"
author: "Nick Bias"
date: "12/7/2021"
output: html_document
---

```{r setup, include=FALSE, error=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(tidymodels)
library(janitor)
library(nnet)
library(parallel)
options(scipen=99)
```
# Data
```{r}
train <- read.csv("train_new.csv")


train <- train %>% 
  clean_names() %>% 
  mutate_if(is.character, factor) %>% 
  mutate(
    bedroom_abv_gr= factor(bedroom_abv_gr),
    yr_sold = factor(yr_sold),
    tot_rms_abv_grd = factor(tot_rms_abv_grd),
    half_bath = factor(half_bath),
    full_bath = factor(full_bath),
    overall_qual = factor(overall_qual),
    overall_cond = factor(overall_cond),
    Age = 2021 - year_built, .before=roof_style,
    log_sale_price = log(sale_price),
    log_lot_frontage = log(lot_frontage),
    log_lot_area = log(lot_area), 
    log_pool_area = log(pool_area),
    log_screen_porch = log(screen_porch),
    log_gr_liv_area = log(gr_liv_area)
  )

train$lot_frontage[is.na(train$lot_frontage)] <- mean(train$lot_frontage, na.rm=TRUE)

summary(train)
```
```{r}
test <- read.csv("test_new.csv")


test <- test %>% 
  clean_names() %>% 
  mutate_if(is.character, factor) %>% 
  mutate(
    bedroom_abv_gr= factor(bedroom_abv_gr),
    yr_sold = factor(yr_sold),
    tot_rms_abv_grd = factor(tot_rms_abv_grd),
    half_bath = factor(half_bath),
    full_bath = factor(full_bath),
    overall_qual = factor(overall_qual),
    overall_cond = factor(overall_cond),
    Age = 2021 - year_built, .before=roof_style,
    log_lot_frontage = log(lot_frontage),
    log_lot_area = log(lot_area), 
    log_pool_area = log(pool_area),
    log_screen_porch = log(screen_porch),
    log_gr_liv_area = log(gr_liv_area)
  )

#train$lot_frontage[is.na(train$lot_frontage)] <- mean(train$lot_frontage, na.rm=TRUE)

summary(test)
```
# Cross Validation dataset
```{r}
set.seed(45623)
train_cv5 <- vfold_cv(train, v = 5)
train_cv10 <- vfold_cv(train, v = 10)
```

# Recipes
```{r}
rec1 <- recipe(log_sale_price ~ lot_frontage+lot_area+street+neighborhood+bldg_type+house_style+overall_qual+overall_cond+year_built+Age+roof_style+heating+central_air+electrical+full_bath+half_bath+bedroom_abv_gr+tot_rms_abv_grd+gr_liv_area+functional+screen_porch+pool_area+yr_sold+sale_type, data= train) %>% 
  step_dummy(all_nominal(), -all_outcomes())

rec1_1 <- recipe(log_sale_price ~ lot_frontage+lot_area+street+neighborhood+bldg_type+house_style+overall_qual+overall_cond+year_built+Age+roof_style+heating+central_air+electrical+full_bath+half_bath+bedroom_abv_gr+tot_rms_abv_grd+gr_liv_area+functional+screen_porch+pool_area+yr_sold+sale_type, data= train) 


rec2 <- recipe(log_sale_price ~ log_lot_frontage+log_lot_area+street+neighborhood+bldg_type+house_style+overall_qual+overall_cond+year_built+Age+roof_style+heating+central_air+electrical+full_bath+half_bath+bedroom_abv_gr+tot_rms_abv_grd+log_gr_liv_area+functional+screen_porch+pool_area+yr_sold+sale_type, data= train) %>% 
  step_dummy(all_nominal(), -all_outcomes())

rec2_1 <- recipe(log_sale_price ~ log_lot_frontage+log_lot_area+street+neighborhood+bldg_type+house_style+overall_qual+overall_cond+year_built+Age+roof_style+heating+central_air+electrical+full_bath+half_bath+bedroom_abv_gr+tot_rms_abv_grd+log_gr_liv_area+functional+screen_porch+pool_area+yr_sold+sale_type, data= train)


rec3 <- recipe(log_sale_price ~ lot_frontage+lot_area+street+neighborhood+bldg_type+house_style+overall_qual+overall_cond+year_built+Age+roof_style+heating+central_air+full_bath+half_bath+gr_liv_area+functional+screen_porch+pool_area+sale_type, data= train) %>% 
  step_dummy(all_nominal(), -all_outcomes())

rec3_1 <- recipe(log_sale_price ~ lot_frontage+lot_area+street+neighborhood+bldg_type+house_style+overall_qual+overall_cond+year_built+Age+roof_style+heating+central_air+full_bath+half_bath+gr_liv_area+functional+screen_porch+pool_area+sale_type, data= train) 


rec4 <- recipe(log_sale_price ~ log_lot_frontage+log_lot_area+street+neighborhood+bldg_type+house_style+overall_qual+overall_cond+year_built+Age+roof_style+heating+central_air+full_bath+half_bath+log_gr_liv_area+functional+screen_porch+pool_area+sale_type, data= train) %>% 
  step_dummy(all_nominal(), -all_outcomes())

rec4_1 <- recipe(log_sale_price ~ log_lot_frontage+log_lot_area+street+neighborhood+bldg_type+house_style+overall_qual+overall_cond+year_built+Age+roof_style+heating+central_air+full_bath+half_bath+log_gr_liv_area+functional+screen_porch+pool_area+sale_type, data= train) 
```

# Plots
## sales
```{r}
train %>% 
  ggplot(aes(x=sale_price))+
  geom_histogram()
```
```{r}
train %>% 
  ggplot(aes(x=log_sale_price))+
  geom_histogram()
```
## lot_frontage
```{r}
train %>% 
  ggplot(aes(x=lot_frontage))+
  geom_histogram()
test %>% 
  ggplot(aes(x=lot_frontage))+
  geom_histogram()
```
```{r}
train %>% 
  ggplot(aes(x=log_lot_frontage))+
  geom_histogram()
test %>% 
  ggplot(aes(x=log_lot_frontage))+
  geom_histogram()
```
## lot_area
```{r}
train %>% 
  ggplot(aes(x=lot_area))+
  geom_histogram()
test %>% 
  ggplot(aes(x=lot_area))+
  geom_histogram()
```
```{r}
train %>% 
  ggplot(aes(x=log_lot_area))+
  geom_histogram()
test %>% 
  ggplot(aes(x=log_lot_area))+
  geom_histogram()
```


## pool_area         
```{r}
train %>% 
  ggplot(aes(x=pool_area))+
  geom_histogram()
test %>% 
  ggplot(aes(x=pool_area))+
  geom_histogram()
```
```{r}
train %>% 
  ggplot(aes(x=log_pool_area))+
  geom_histogram()
test %>% 
  ggplot(aes(x=log_pool_area))+
  geom_histogram()
```
## screen_porch
```{r}
train %>% 
  ggplot(aes(x=screen_porch))+
  geom_histogram()
test %>% 
  ggplot(aes(x=screen_porch))+
  geom_histogram()
```
```{r}
train %>% 
  ggplot(aes(x=log_screen_porch))+
  geom_histogram()
test %>% 
  ggplot(aes(x=log_screen_porch))+
  geom_histogram()
```





## gr_liv_area
```{r}
train %>% 
  ggplot(aes(x=gr_liv_area))+
  geom_histogram()
test %>% 
  ggplot(aes(x=gr_liv_area))+
  geom_histogram()
```
```{r}
train %>% 
  ggplot(aes(x=log_gr_liv_area))+
  geom_histogram()
test %>% 
  ggplot(aes(x=log_gr_liv_area))+
  geom_histogram()
```



 
house size and bedrooms 

# Significant Variables
```{r}
lr_mod <- linear_reg() %>%
  set_mode("regression") %>%
  set_engine("lm")

wflow <- workflow() %>% 
  add_model(lr_mod) %>% 
  add_recipe(rec1)

model_fit <- wflow %>% 
  fit(train)

wflow_fit <- model_fit %>% pull_workflow_fit() 
wflow_fit$fit %>% summary()
```
```{r}
lr_mod <- linear_reg() %>%
  set_mode("regression") %>%
  set_engine("lm")

wflow <- workflow() %>% 
  add_model(lr_mod) %>% 
  add_recipe(rec2)

model_fit <- wflow %>% 
  fit(train)

wflow_fit <- model_fit %>% pull_workflow_fit() 
wflow_fit$fit %>% summary()
```




# Models
## Linear Regression


```{r}
lr_mod <- linear_reg() %>%
  set_mode("regression") %>%
  set_engine("lm")

lr_rec1_5 <- lr_mod %>% 
  fit_resamples(rec1,
                resamples = train_cv5,
                control = control_resamples(save_pred = TRUE))

lr_rec1_1_5 <- lr_mod %>% 
  fit_resamples(rec1_1,
                resamples = train_cv5,
                control = control_resamples(save_pred = TRUE))


lr_rec2_5 <- lr_mod %>% 
  fit_resamples(rec2,
                resamples = train_cv5,
                control = control_resamples(save_pred = TRUE))

lr_rec2_1_5 <- lr_mod %>% 
  fit_resamples(rec2_1,
                resamples = train_cv5,
                control = control_resamples(save_pred = TRUE))


lr_rec3_5 <- lr_mod %>% 
  fit_resamples(rec3,
                resamples = train_cv5,
                control = control_resamples(save_pred = TRUE))

lr_rec3_1_5 <- lr_mod %>% 
  fit_resamples(rec3_1,
                resamples = train_cv5,
                control = control_resamples(save_pred = TRUE))


lr_rec4_5 <- lr_mod %>% 
  fit_resamples(rec4,
                resamples = train_cv5,
                control = control_resamples(save_pred = TRUE))

lr_rec4_1_5 <- lr_mod %>% 
  fit_resamples(rec4_1,
                resamples = train_cv5,
                control = control_resamples(save_pred = TRUE))
```
```{r}
lr1 <- lr_rec1_5 %>% collect_metrics() %>% mutate(Model="LR-1", .before=.metric)
lr1_1 <- lr_rec1_1_5 %>% collect_metrics() %>% mutate(Model="LR-1-1", .before=.metric)

lr2 <- lr_rec2_5 %>% collect_metrics() %>% mutate(Model="LR-2", .before=.metric)
lr2_1 <- lr_rec2_1_5 %>% collect_metrics() %>% mutate(Model="LR-2-1", .before=.metric)

lr3 <- lr_rec3_5 %>% collect_metrics() %>% mutate(Model="LR-3", .before=.metric)
lr3_1 <- lr_rec3_1_5 %>% collect_metrics() %>% mutate(Model="LR-3-1", .before=.metric)

lr4 <- lr_rec4_5 %>% collect_metrics() %>% mutate(Model="LR-4", .before=.metric)
lr4_1 <- lr_rec4_1_5 %>% collect_metrics() %>% mutate(Model="LR-4-1", .before=.metric)
```

```{r}
lr_Comp <- rbind(lr1, lr1_1, lr2, lr2_1, lr3, lr3_1, lr4, lr4_1) %>% 
  dplyr::select(Model, .metric, mean) %>% 
  pivot_wider(names_from = .metric,
              values_from = mean)

lr_Comp
```
```{r}
lr_rec1_10 <- lr_mod %>% 
  fit_resamples(rec1,
                resamples = train_cv10,
                control = control_resamples(save_pred = TRUE))

lr_rec1_1_10 <- lr_mod %>% 
  fit_resamples(rec1_1,
                resamples = train_cv10,
                control = control_resamples(save_pred = TRUE))


lr_rec2_10 <- lr_mod %>% 
  fit_resamples(rec2,
                resamples = train_cv10,
                control = control_resamples(save_pred = TRUE))

lr_rec2_1_10 <- lr_mod %>% 
  fit_resamples(rec2_1,
                resamples = train_cv10,
                control = control_resamples(save_pred = TRUE))


lr_rec3_10 <- lr_mod %>% 
  fit_resamples(rec3,
                resamples = train_cv10,
                control = control_resamples(save_pred = TRUE))

lr_rec3_1_10 <- lr_mod %>% 
  fit_resamples(rec3_1,
                resamples = train_cv10,
                control = control_resamples(save_pred = TRUE))


lr_rec4_10 <- lr_mod %>% 
  fit_resamples(rec4,
                resamples = train_cv10,
                control = control_resamples(save_pred = TRUE))

lr_rec4_1_10 <- lr_mod %>% 
  fit_resamples(rec4_1,
                resamples = train_cv10,
                control = control_resamples(save_pred = TRUE))
```
```{r}
lr1_10 <- lr_rec1_10 %>% collect_metrics() %>% mutate(Model="LR-1_10", .before=.metric)
lr1_1_10 <- lr_rec1_1_10 %>% collect_metrics() %>% mutate(Model="LR-1-1_10", .before=.metric)

lr2_10 <- lr_rec2_10 %>% collect_metrics() %>% mutate(Model="LR-2_10", .before=.metric)
lr2_1_10 <- lr_rec2_1_10 %>% collect_metrics() %>% mutate(Model="LR-2-1_10", .before=.metric)

lr3_10 <- lr_rec3_10 %>% collect_metrics() %>% mutate(Model="LR-3_10", .before=.metric)
lr3_1_10 <- lr_rec3_1_10 %>% collect_metrics() %>% mutate(Model="LR-3-1_10", .before=.metric)

lr4_10 <- lr_rec4_10 %>% collect_metrics() %>% mutate(Model="LR-4_10", .before=.metric)
lr4_1_10 <- lr_rec4_1_10 %>% collect_metrics() %>% mutate(Model="LR-4-1_10", .before=.metric)
```

```{r}
lr_Comp <- rbind(lr1_10, lr1_1_10, lr2_10, lr2_1_10, lr3_10, lr3_1_10, lr4_10, lr4_1_10) %>% 
  dplyr::select(Model, .metric, mean) %>% 
  pivot_wider(names_from = .metric,
              values_from = mean)

lr_Comp
```

**Linear Regression Model 4_1** seems to be performing the best
lr4_1_10
lr4_1

## Regression Tree
```{r}
tree_grid <- grid_regular(cost_complexity(),
                          tree_depth(),
                          min_n(), 
                          levels = 2)

tree_mod <- decision_tree(cost_complexity = tune(),
                          tree_depth = tune(),
                          min_n = tune()) %>%
  set_engine("rpart") %>%
  set_mode("regression")

tree_wflow <- workflow() %>%
  add_recipe(rec3) %>%
  add_model(tree_mod)
```

```{r}
tree_grid_search <-
  tune_grid(
    tree_wflow,
    resamples = train_cv5,
    grid = tree_grid
  )
```

```{r}
tuning_metrics <- tree_grid_search %>% collect_metrics()
tuning_metrics
```

```{r}
tree_mod <- decision_tree(cost_complexity = 0.0000000001,
                          tree_depth = 15,
                          min_n = 40) %>%
  set_engine("rpart") %>%
  set_mode("regression")

tree_rec1_5 <- tree_mod %>% 
  fit_resamples(rec1,
                resamples = train_cv5,
                control = control_resamples(save_pred = TRUE))

tree_rec1_1_5 <- tree_mod %>% 
  fit_resamples(rec1_1,
                resamples = train_cv5,
                control = control_resamples(save_pred = TRUE))


tree_rec2_5 <- tree_mod %>% 
  fit_resamples(rec2,
                resamples = train_cv5,
                control = control_resamples(save_pred = TRUE))

tree_rec2_1_5 <- tree_mod %>% 
  fit_resamples(rec2_1,
                resamples = train_cv5,
                control = control_resamples(save_pred = TRUE))


tree_rec3_5 <- tree_mod %>% 
  fit_resamples(rec3,
                resamples = train_cv5,
                control = control_resamples(save_pred = TRUE))

tree_rec3_1_5 <- tree_mod %>% 
  fit_resamples(rec3_1,
                resamples = train_cv5,
                control = control_resamples(save_pred = TRUE))


tree_rec4_5 <- tree_mod %>% 
  fit_resamples(rec4,
                resamples = train_cv5,
                control = control_resamples(save_pred = TRUE))

tree_rec4_1_5 <- tree_mod %>% 
  fit_resamples(rec4_1,
                resamples = train_cv5,
                control = control_resamples(save_pred = TRUE))
```


```{r}
tr1 <- tree_rec1_5 %>% collect_metrics() %>% mutate(Model="Tree-1", .before=.metric)
tr1_1 <- tree_rec1_1_5 %>% collect_metrics() %>% mutate(Model="Tree-1-1", .before=.metric)

tr2 <- tree_rec2_5 %>% collect_metrics() %>% mutate(Model="Tree-2", .before=.metric)
tr2_1 <- tree_rec2_1_5 %>% collect_metrics() %>% mutate(Model="Tree-2-1", .before=.metric)

tr3 <- tree_rec3_5 %>% collect_metrics() %>% mutate(Model="Tree-3", .before=.metric)
tr3_1 <- tree_rec3_1_5 %>% collect_metrics() %>% mutate(Model="Tree-3-1", .before=.metric)

tr4 <- tree_rec4_5 %>% collect_metrics() %>% mutate(Model="Tree-4", .before=.metric)
tr4_1 <- tree_rec4_1_5 %>% collect_metrics() %>% mutate(Model="Tree-4-1", .before=.metric)
```

```{r}
tr_Comp <- rbind(tr1, tr1_1, tr2, tr2_1, tr3, tr3_1, tr4, tr4_1) %>% 
  dplyr::select(Model, .metric, mean) %>% 
  pivot_wider(names_from = .metric,
              values_from = mean)

tr_Comp
```
**Tree 3-1** seems to be performing the best

```{r}
tree_rec1_10 <- tree_mod %>% 
  fit_resamples(rec1,
                resamples = train_cv10,
                control = control_resamples(save_pred = TRUE))

tree_rec1_1_10 <- tree_mod %>% 
  fit_resamples(rec1_1,
                resamples = train_cv10,
                control = control_resamples(save_pred = TRUE))


tree_rec2_10 <- tree_mod %>% 
  fit_resamples(rec2,
                resamples = train_cv10,
                control = control_resamples(save_pred = TRUE))

tree_rec2_1_10 <- tree_mod %>% 
  fit_resamples(rec2_1,
                resamples = train_cv10,
                control = control_resamples(save_pred = TRUE))


tree_rec3_10 <- tree_mod %>% 
  fit_resamples(rec3,
                resamples = train_cv10,
                control = control_resamples(save_pred = TRUE))

tree_rec3_1_10 <- tree_mod %>% 
  fit_resamples(rec3_1,
                resamples = train_cv10,
                control = control_resamples(save_pred = TRUE))


tree_rec4_10 <- tree_mod %>% 
  fit_resamples(rec4,
                resamples = train_cv10,
                control = control_resamples(save_pred = TRUE))

tree_rec4_1_10 <- tree_mod %>% 
  fit_resamples(rec4_1,
                resamples = train_cv10,
                control = control_resamples(save_pred = TRUE))
```

```{r}
tr1_10 <- tree_rec1_10 %>% collect_metrics() %>% mutate(Model="Tree-1_10", .before=.metric)
tr1_1_10 <- tree_rec1_1_10 %>% collect_metrics() %>% mutate(Model="Tree-1-1_10", .before=.metric)

tr2_10 <- tree_rec2_10 %>% collect_metrics() %>% mutate(Model="Tree-2_10", .before=.metric)
tr2_1_10 <- tree_rec2_1_10 %>% collect_metrics() %>% mutate(Model="Tree-2-1_10", .before=.metric)

tr3_10 <- tree_rec3_10 %>% collect_metrics() %>% mutate(Model="Tree-3_10", .before=.metric)
tr3_1_10 <- tree_rec3_1_10 %>% collect_metrics() %>% mutate(Model="Tree-3-1_10", .before=.metric)

tr4_10 <- tree_rec4_10 %>% collect_metrics() %>% mutate(Model="Tree-4_10", .before=.metric)
tr4_1_10 <- tree_rec4_1_10 %>% collect_metrics() %>% mutate(Model="Tree-4-1_10", .before=.metric)
```

```{r}
tr_Comp_10 <- rbind(tr1_10, tr1_1_10, tr2_10, tr2_1_10, tr3_10, tr3_1_10, tr4_10, tr4_1_10) %>% 
  dplyr::select(Model, .metric, mean) %>% 
  pivot_wider(names_from = .metric,
              values_from = mean)

tr_Comp_10
```

Overall, Decision Tree is not performing as well as linear regression



## Model that dont work
### Random Forest
```{r, error=TRUE}
cores <- detectCores()

rf_mod <- 
  rand_forest(mtry = tune(), min_n = tune(), trees = 1000) %>% 
  set_engine("ranger", num.threads = cores) %>% 
  set_mode("regression")

rf_res <- rf_mod %>% 
  tune_grid(rec4,
            resamples = train_cv5,
            grid = 10,
            control = control_grid(save_pred = TRUE))
  
tuning_metrics2 <- rf_res %>% collect_metrics()

tuning_metrics2 %>% 
  filter(.metric == "rmse") %>% 
  slice_min(mean)
```
```{r, error=TRUE}
cores <- detectCores()
rf_mod <- 
  rand_forest(mtry = 15, min_n = 36, trees = 1000) %>% 
  set_engine("ranger", num.threads = cores) %>% 
  set_mode("regression")

rf_rec1 <- rf_mod %>% 
  fit_resamples(rec1, 
                resamples = train_cv5, 
                control = control_resamples(save_pred = TRUE)) 
rf_rec1_1 <- rf_mod %>% 
  fit_resamples(rec1_1, 
                resamples = train_cv5, 
                control = control_resamples(save_pred = TRUE)) 

rf_rec2 <- rf_mod %>% 
  fit_resamples(rec2, 
                resamples = train_cv5, 
                control = control_resamples(save_pred = TRUE)) 
rf_rec2_1 <- rf_mod %>% 
  fit_resamples(rec2_1, 
                resamples = train_cv5, 
                control = control_resamples(save_pred = TRUE)) 

rf_rec3 <- rf_mod %>% 
  fit_resamples(rec3, 
                resamples = train_cv5, 
                control = control_resamples(save_pred = TRUE)) 
rf_rec3_1 <- rf_mod %>% 
  fit_resamples(rec3_1, 
                resamples = train_cv5, 
                control = control_resamples(save_pred = TRUE)) 

rf_rec4 <- rf_mod %>% 
  fit_resamples(rec4, 
                resamples = train_cv5, 
                control = control_resamples(save_pred = TRUE)) 
rf_rec4_1 <- rf_mod %>% 
  fit_resamples(rec4_1, 
                resamples = train_cv5, 
                control = control_resamples(save_pred = TRUE)) 
```

```{r, error=TRUE}
rf1 <- rf_rec1 %>% collect_metrics() %>% mutate(Model="RF-1", .before=.metric)
rf1_1 <- rf_rec1_1 %>% collect_metrics() %>% mutate(Model="RF-1_1", .before=.metric)
rf2 <- rf_rec2 %>% collect_metrics() %>% mutate(Model="RF-2", .before=.metric)
rf2_1 <- rf_rec2_1 %>% collect_metrics() %>% mutate(Model="RF-2_1", .before=.metric)
rf3 <- rf_rec3 %>% collect_metrics() %>% mutate(Model="RF-3", .before=.metric)
rf3_1 <- rf_rec3_1 %>% collect_metrics() %>% mutate(Model="RF-3_1", .before=.metric)
rf4 <- rf_rec4 %>% collect_metrics() %>% mutate(Model="RF-4", .before=.metric)
rf4_1 <- rf_rec4_1 %>% collect_metrics() %>% mutate(Model="RF-4_1", .before=.metric)

tree_Comp <- rbind(rf1, rf1_1) %>% 
  dplyr::select(Model, .metric, mean) %>% 
  pivot_wider(names_from = .metric,
              values_from = mean)
tree_Comp
```

Random Forest does not seem to work 



### Bagging?
```{r}
library(baguette)
bag_tree_spec <- bag_tree() %>%
  set_engine("rpart", times = 25) %>%
  set_mode("regression")

bag_fit1 <- bag_tree_spec %>% 
  fit_resamples(rec1, 
                resample = train_cv5,
                control = control_resamples(save_pred = TRUE))
bag_fit1_1 <- bag_tree_spec %>% 
  fit_resamples(rec1_1, 
                resample = train_cv5,
                control = control_resamples(save_pred = TRUE))

bag_fit2 <- bag_tree_spec %>% 
  fit_resamples(rec2, 
                resample = train_cv5,
                control = control_resamples(save_pred = TRUE))
bag_fit2_1 <- bag_tree_spec %>% 
  fit_resamples(rec2_1, 
                resample = train_cv5,
                control = control_resamples(save_pred = TRUE))

bag_fit3 <- bag_tree_spec %>% 
  fit_resamples(rec3, 
                resample = train_cv5,
                control = control_resamples(save_pred = TRUE))
bag_fit3_1 <- bag_tree_spec %>% 
  fit_resamples(rec3_1, 
                resample = train_cv5,
                control = control_resamples(save_pred = TRUE))

bag_fit4 <- bag_tree_spec %>% 
  fit_resamples(rec4, 
                resample = train_cv5,
                control = control_resamples(save_pred = TRUE))
bag_fit4_1 <- bag_tree_spec %>% 
  fit_resamples(rec4_1, 
                resample = train_cv5,
                control = control_resamples(save_pred = TRUE))
```
```{r}
bag1 <- bag_fit1 %>% collect_metrics() %>% mutate(Model="Bag-2", .before=.metric)
bag1_1 <- bag_fit1_1 %>% collect_metrics() %>% mutate(Model="Bag-2-1", .before=.metric)

bag2 <- bag_fit2 %>% collect_metrics() %>% mutate(Model="Bag-2", .before=.metric)
bag2_1 <- bag_fit2_1 %>% collect_metrics() %>% mutate(Model="Bag-2-1", .before=.metric)

bag3 <- bag_fit3 %>% collect_metrics() %>% mutate(Model="Bag-3", .before=.metric)
bag3_1 <- bag_fit3_1 %>% collect_metrics() %>% mutate(Model="Bag-3-1", .before=.metric)

bag4 <- bag_fit4 %>% collect_metrics() %>% mutate(Model="Bag-4", .before=.metric)
bag4_1 <- bag_fit4_1 %>% collect_metrics() %>% mutate(Model="Bag-4-1", .before=.metric)
```

```{r}
lr_Comp <- rbind(bag1, bag1_1, bag2, bag2_1, bag3, bag3_1, bag4, bag4_1) %>% 
  dplyr::select(Model, .metric, mean) %>% 
  pivot_wider(names_from = .metric,
              values_from = mean)

lr_Comp
```
Bagging is also not working 

### Nueral Network
```{r, error=TRUE}
nn_mod <- mlp(
  hidden_units = 12,
  penalty = 1,
  epochs = 100,
  activation = "linear") %>%
  set_engine("nnet") %>%
  set_mode("regression")

nn_rec1 <- nn_mod %>% 
  fit_resamples(rec1, 
                resamples = train_cv5, 
                control = control_resamples(save_pred = TRUE)) 
nn_rec1_1 <- nn_mod %>% 
  fit_resamples(rec1_1, 
                resamples = train_cv5, 
                control = control_resamples(save_pred = TRUE)) 

nn_rec2 <- nn_mod %>% 
  fit_resamples(rec2, 
                resamples = train_cv5, 
                control = control_resamples(save_pred = TRUE)) 
nn_rec2_1 <- nn_mod %>% 
  fit_resamples(rec2_1, 
                resamples = train_cv5, 
                control = control_resamples(save_pred = TRUE)) 

nn_rec3 <- nn_mod %>% 
  fit_resamples(rec3, 
                resamples = train_cv5, 
                control = control_resamples(save_pred = TRUE)) 
nn_rec3_1 <- nn_mod %>% 
  fit_resamples(rec3_1, 
                resamples = train_cv5, 
                control = control_resamples(save_pred = TRUE)) 

nn_rec4 <- nn_mod %>% 
  fit_resamples(rec4, 
                resamples = train_cv5, 
                control = control_resamples(save_pred = TRUE)) 
nn_rec4_1 <- nn_mod %>% 
  fit_resamples(rec4_1, 
                resamples = train_cv5, 
                control = control_resamples(save_pred = TRUE)) 

nn1 <- nn_rec1 %>% collect_metrics() %>% mutate(Model="NN-1", .before=.metric)
nn1_1 <- nn_rec1_1 %>% collect_metrics() %>% mutate(Model="NN-1_1", .before=.metric)
nn2 <- nn_rec2 %>% collect_metrics() %>% mutate(Model="NN-2", .before=.metric)
nn2_1 <- nn_rec2_1 %>% collect_metrics() %>% mutate(Model="NN-2_1", .before=.metric)
nn3 <- nn_rec3 %>% collect_metrics() %>% mutate(Model="NN-3", .before=.metric)
nn3_1 <- nn_rec3_1 %>% collect_metrics() %>% mutate(Model="NN-3_1", .before=.metric)
nn4 <- nn_rec4 %>% collect_metrics() %>% mutate(Model="NN-4", .before=.metric)
nn4_1 <- nn_rec4_1 %>% collect_metrics() %>% mutate(Model="NN-4_1", .before=.metric)

nn_Comp <- rbind(nn1, nn1_1, nn2, nn2_1, nn3, nn3_1, nn4, nn4_1) %>% 
  dplyr::select(Model, .metric, mean) %>% 
  pivot_wider(names_from = .metric,
              values_from = mean)
nn_Comp
```

# Model Comparisions 
```{r}
model_Comp <- rbind(lr4_1, lr4_1_10, tr3_1, tr4_1, tr4_1_10) %>% 
  dplyr::select(Model, .metric, mean) %>% 
  pivot_wider(names_from = .metric,
              values_from = mean)

model_Comp
```
# Final Model
```{r}
rec4_1 <- recipe(log_sale_price ~ log_lot_frontage+log_lot_area+street+neighborhood+bldg_type+house_style+overall_qual+overall_cond+year_built+Age+roof_style+heating+central_air+full_bath+half_bath+log_gr_liv_area+functional+screen_porch+pool_area+sale_type, data= train) 

lr_mod <- linear_reg() %>%
  set_mode("regression") %>%
  set_engine("lm")

wflow <- workflow() %>%
  add_model(lr_mod) %>%
  add_recipe(rec4_1) 

lr_final <- wflow %>% fit(train)
```

```{r}
predictions <- predict(lr_final, new_data = test)
SalePricePrediction <- exp(predictions)

final_predictions <- data.frame(
    PID  = test$pid,
    SalePrice = SalePricePrediction
)
```
```{r}
final_predictions <- final_predictions %>% 
  mutate(
    SalePrice = .pred
  ) 
```


```{r}
final_predictions <- final_predictions[,-2]
```

```{r}
final_predictions %>% write_csv("NickBias_QuantitativePredictions.csv")
```

