---
title: "Final_Cat"
author: "Nick Bias"
date: "12/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = TRUE)
```

```{r, message=FALSE}
library(tidyverse)
library(tidymodels)
library(rpart.plot)
library(discrim)
library(baguette)
library(janitor)
library(vip)
library(kknn)
library(parallel)
library(nnet)
options(scipen=99)
```


# Load & Clean Data
```{r}
train <- read.csv("CAH-201803-train.csv")

train <- train %>% 
  mutate(
    Q1 = factor(Q1),
    political_affiliation = factor(political_affiliation),
    Q4 = factor(Q4),
    Q5 = factor(Q5),
    Q6 = factor(Q6),
    Q7 = factor(Q7),
    Q8 = factor(Q8),
    Q9 = factor(Q9),
    Q10 = factor(Q10),
    Q11 = factor(Q11),
    Q12 = factor(Q12),
    Q13 = factor(Q13),
    Q14 = factor(Q14),
    Q15 = factor(Q15),
    Q16 = factor(Q16),
    Q17 = factor(Q17),
    Q18 = factor(Q18)
  )
```

```{r}
summary(train)
```

# Cross Validation dataset
```{r}
set.seed(1)
train_cv5 <- vfold_cv(train, v = 5)
```

# Recipes 
```{r}
rec1 <- recipe(political_affiliation ~ ., data = train)

rec2 <- recipe(political_affiliation ~ ., data = train) %>% 
  step_dummy(all_nominal(), -all_outcomes())

rec3 <- recipe(political_affiliation ~ ., data = train) %>% 
  step_normalize(all_numeric()) %>% 
  step_dummy(all_nominal(), -all_outcomes())

rec4 <- recipe(political_affiliation ~ Q2 + Q4 + Q6 + Q10 + Q15 + Q17 + Q18, data = train)

rec5 <- recipe(political_affiliation ~ Q2 + Q4 + Q6 + Q10 + Q15 + Q17 + Q18, data = train)%>% 
  step_dummy(all_nominal(), -all_outcomes())

rec6 <- recipe(political_affiliation ~ Q2 + Q4 + Q6 + Q10 + Q15 + Q17 + Q18, data = train)%>% 
  step_dummy(all_nominal(), -all_outcomes()) %>% 
  step_dummy(all_nominal(), -all_outcomes())
```


# Models 

### Logistic Regression
```{r}
log_reg_spec <- logistic_reg() %>%
  set_engine("glm") %>%
  set_mode("classification")

wflow <- workflow() %>% 
  add_model(log_reg_spec) %>% 
  add_recipe(rec1)

model_fit <- wflow %>% 
  fit(train)

wflow_fit <- model_fit %>% pull_workflow_fit() 
wflow_fit$fit %>% summary()
```

``{r}
train_fit <- log_reg_spec %>%
  fit_resamples(rec1, 
                resamples = train_cv5,
                
                control = control_resamples(save_pred = TRUE))

lr <- train_fit %>% collect_metrics() %>% mutate(Model="Logistic Regression", .before=.metric)
lr
``
Wont work because logistic regression is for binary classification 

### KNN
```{r}
knn_mod <- nearest_neighbor(neighbors = 35) %>%
  set_engine("kknn") %>%
  set_mode("classification")

knn_rec1 <- knn_mod %>% 
  fit_resamples(rec1, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
knn_rec2 <- knn_mod %>% 
  fit_resamples(rec2, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
knn_rec3 <- knn_mod %>% 
  fit_resamples(rec3, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
knn_rec4 <- knn_mod %>% 
  fit_resamples(rec4, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
knn_rec5 <- knn_mod %>% 
  fit_resamples(rec5, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
knn_rec6 <- knn_mod %>% 
  fit_resamples(rec6, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 

knn1 <- knn_rec1 %>% collect_metrics() %>% mutate(Model="KNN-1", .before=.metric)
knn2 <- knn_rec2 %>% collect_metrics() %>% mutate(Model="KNN-2", .before=.metric)
knn3 <- knn_rec3 %>% collect_metrics() %>% mutate(Model="KNN-3", .before=.metric)
knn4 <- knn_rec4 %>% collect_metrics() %>% mutate(Model="KNN-4", .before=.metric)
knn5 <- knn_rec5 %>% collect_metrics() %>% mutate(Model="KNN-5", .before=.metric)
knn6 <- knn_rec6 %>% collect_metrics() %>% mutate(Model="KNN-6", .before=.metric)
```

```{r}
Model_Comp <- rbind(knn1, knn2, knn3, knn4, knn5, knn6) %>% 
  dplyr::select(Model, .metric, mean) %>% 
  pivot_wider(names_from = .metric,
              values_from = mean)

Model_Comp
```

**KNN-4 is the winner**
knn_wflow <- workflow() %>% 
  add_model(knn_mod) %>% 
  add_recipe(rec)
  
```{r}
knn_mod_tune <- nearest_neighbor(neighbors = tune()) %>%
  set_engine("kknn") %>%
  set_mode("classification")

k_grid <- grid_regular(neighbors(c(1,50)),
                       levels = 11)

knn_tune_wf <- workflow() %>% 
  add_model(knn_mod_tune) %>% 
  add_recipe(rec5)

knn_grid_search2 <-
  tune_grid(
    knn_tune_wf,
    resamples = train_cv5,
    grid = k_grid
  )
```

```{r}
knn_grid_search2 %>% collect_metrics()
```
K = 35


### LDA
```{r}
lda_mod <- discrim_linear() %>%
  set_engine("MASS") %>%
  set_mode("classification")

lda_rec1 <- lda_mod %>% 
  fit_resamples(rec1, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
lda_rec2 <- lda_mod %>% 
  fit_resamples(rec2, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
lda_rec3 <- lda_mod %>% 
  fit_resamples(rec3, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
lda_rec4 <- lda_mod %>% 
  fit_resamples(rec4, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
lda_rec5 <- lda_mod %>% 
  fit_resamples(rec5, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
lda_rec6 <- lda_mod %>% 
  fit_resamples(rec6, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
```

```{r}
lda1 <- lda_rec1 %>% collect_metrics() %>% mutate(Model="LDA-1", .before=.metric)
lda2 <- lda_rec2 %>% collect_metrics() %>% mutate(Model="LDA-2", .before=.metric)
lda3 <- lda_rec3 %>% collect_metrics() %>% mutate(Model="LDA-3", .before=.metric)
lda4 <- lda_rec4 %>% collect_metrics() %>% mutate(Model="LDA-4", .before=.metric)
lda5 <- lda_rec5 %>% collect_metrics() %>% mutate(Model="LDA-5", .before=.metric)
lda6 <- lda_rec6 %>% collect_metrics() %>% mutate(Model="LDA-6", .before=.metric)

lda_Comp <- rbind(lda1, lda2, lda3, lda4, lda5, lda6) %>% 
  dplyr::select(Model, .metric, mean) %>% 
  pivot_wider(names_from = .metric,
              values_from = mean)
lda_Comp
```

Not much of difference 
LDA-1 
LDA-4

### QDA
```{r}
qda_mod <- discrim_regularized(frac_common_cov = 0) %>% 
             set_engine('klaR') %>% 
             set_mode('classification')

qda_rec1 <- qda_mod %>% 
  fit_resamples(rec1, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
qda_rec2 <- qda_mod %>% 
  fit_resamples(rec2, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
qda_rec3 <- qda_mod %>% 
  fit_resamples(rec3, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
qda_rec4 <- qda_mod %>% 
  fit_resamples(rec4, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
qda_rec5 <- qda_mod %>% 
  fit_resamples(rec5, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
qda_rec6 <- qda_mod %>% 
  fit_resamples(rec6, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
```

```{r}
qda1 <- qda_rec1 %>% collect_metrics() %>% mutate(Model="QDA-1", .before=.metric)
qda2 <- qda_rec2 %>% collect_metrics() %>% mutate(Model="QDA-2", .before=.metric)
qda3 <- qda_rec3 %>% collect_metrics() %>% mutate(Model="QDA-3", .before=.metric)
qda4 <- qda_rec4 %>% collect_metrics() %>% mutate(Model="QDA-4", .before=.metric)
qda5 <- qda_rec5 %>% collect_metrics() %>% mutate(Model="QDA-5", .before=.metric)
qda6 <- qda_rec6 %>% collect_metrics() %>% mutate(Model="QDA-6", .before=.metric)

qda_Comp <- rbind(qda1, qda2, qda3, qda4, qda5, qda6) %>% 
  dplyr::select(Model, .metric, mean) %>% 
  pivot_wider(names_from = .metric,
              values_from = mean)
qda_Comp
```
**QDA-5**


### SVM 
```{r}
svm_spec <- svm_poly(cost = tune(), degree = 1) %>%
  set_mode("classification") %>%
  set_engine("kernlab")


k_grid <- grid_regular(cost(),
                       levels = 10)

fed_wflow <- workflow() %>%
  add_model(svm_spec) %>%
  add_recipe(rec1)

knn_grid_search1 <-
  tune_grid(
    fed_wflow,
    resamples = train_cv5,
    grid = k_grid
  )

tuning_metrics <- knn_grid_search1 %>% collect_metrics()

tuning_metrics %>% 
  filter(.metric == "accuracy") %>% 
  slice_max(mean)
```


```{r}
svm_spec <- svm_poly(cost = 0.09921257, degree = 1) %>%
  set_mode("classification") %>%
  set_engine("kernlab")

svm_rec1 <- svm_spec %>% 
  fit_resamples(rec1, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
svm_rec2 <- svm_spec %>% 
  fit_resamples(rec2, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
svm_rec3 <- svm_spec %>% 
  fit_resamples(rec3, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
svm_rec4 <- svm_spec %>% 
  fit_resamples(rec4, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
svm_rec5 <- svm_spec %>% 
  fit_resamples(rec5, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
svm_rec6 <- svm_spec %>% 
  fit_resamples(rec6, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE))
```

```{r}
svm1 <- svm_rec1 %>% collect_metrics() %>% mutate(Model="SVM-1", .before=.metric)
svm2 <- svm_rec2 %>% collect_metrics() %>% mutate(Model="SVM-2", .before=.metric)
svm3 <- svm_rec3 %>% collect_metrics() %>% mutate(Model="SVM-3", .before=.metric)
svm4 <- svm_rec4 %>% collect_metrics() %>% mutate(Model="SVM-4", .before=.metric)
svm5 <- svm_rec5 %>% collect_metrics() %>% mutate(Model="SVM-5", .before=.metric)
svm6 <- svm_rec6 %>% collect_metrics() %>% mutate(Model="SVM-6", .before=.metric)

svm_Comp <- rbind(svm1, svm2, svm3, svm4, svm5, svm6) %>% 
  dplyr::select(Model, .metric, mean) %>% 
  pivot_wider(names_from = .metric,
              values_from = mean)
svm_Comp
```

**SVM-1**

### PCA
``{r}
pca_rec1 <- recipe(political_affiliation ~ ., data = train) %>% 
  step_pca(all_predictors())

knn_mod_tune <- nearest_neighbor(neighbors = tune()) %>%
  set_engine("kknn") %>%
  set_mode("classification")

k_grid <- grid_regular(neighbors(c(1,10)),
                       levels = 10)

wflow_knn_tune <- workflow() %>% 
  add_model(knn_mod_tune) %>% 
  add_recipe(pca_rec1)

knn_grid_search1 <-
  tune_grid(
    wflow_knn_tune,
    resamples = train_cv5,
    grid = k_grid
  )

knn_grid_search1 %>% collect_metrics()
``

Wont work. All columns selected for the step should be numeric


### Decision Tree
```{r}
tree_mod <- decision_tree() %>%
  set_engine("rpart") %>%
  set_mode("classification")

tree_rec1 <- tree_mod %>% 
  fit_resamples(rec1, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
tree_rec2 <- tree_mod %>% 
  fit_resamples(rec2, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
tree_rec3 <- tree_mod %>% 
  fit_resamples(rec3, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
tree_rec4 <- tree_mod %>% 
  fit_resamples(rec4, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
tree_rec5 <- tree_mod %>% 
  fit_resamples(rec5, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
tree_rec6 <- tree_mod %>% 
  fit_resamples(rec6, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
```

```{r}
tree1 <- tree_rec1 %>% collect_metrics() %>% mutate(Model="Tree-1", .before=.metric)
tree2 <- tree_rec2 %>% collect_metrics() %>% mutate(Model="Tree-2", .before=.metric)
tree3 <- tree_rec3 %>% collect_metrics() %>% mutate(Model="Tree-3", .before=.metric)
tree4 <- tree_rec4 %>% collect_metrics() %>% mutate(Model="Tree-4", .before=.metric)
tree5 <- tree_rec5 %>% collect_metrics() %>% mutate(Model="Tree-5", .before=.metric)
tree6 <- tree_rec6 %>% collect_metrics() %>% mutate(Model="Tree-6", .before=.metric)

tree_Comp <- rbind(tree1, tree2, tree3, tree4, tree5, tree6) %>% 
  dplyr::select(Model, .metric, mean) %>% 
  pivot_wider(names_from = .metric,
              values_from = mean)
tree_Comp
```
Tree-5 

```{r}
tree_grid <- grid_regular(cost_complexity(),
                          tree_depth(),
                          min_n(), 
                          levels = 2)

tree_mod2 <- decision_tree(cost_complexity = tune(),
                          tree_depth = tune(),
                          min_n = tune()) %>%
  set_engine("rpart") %>%
  set_mode("classification")

tree_wflow2 <- workflow() %>%
  add_recipe(rec5) %>%
  add_model(tree_mod2)

tree_grid_search <-
  tune_grid(
    tree_wflow2,
    resamples = train_cv5,
    grid = tree_grid
  )

tuning_metrics <- tree_grid_search %>% collect_metrics()
tuning_metrics %>% 
  filter(.metric == "accuracy") %>% 
  slice_max(mean)
```

```{r}
tree_mod <- decision_tree(cost_complexity = 0.0000000001,
                          tree_depth = 1,
                          min_n = 40) %>%
  set_engine("rpart") %>%
  set_mode("classification")

tree_rec1 <- tree_mod %>% 
  fit_resamples(rec1, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
tree_rec2 <- tree_mod %>% 
  fit_resamples(rec2, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
tree_rec3 <- tree_mod %>% 
  fit_resamples(rec3, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
tree_rec4 <- tree_mod %>% 
  fit_resamples(rec4, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
tree_rec5 <- tree_mod %>% 
  fit_resamples(rec5, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
tree_rec6 <- tree_mod %>% 
  fit_resamples(rec6, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
```

```{r}
tree1 <- tree_rec1 %>% collect_metrics() %>% mutate(Model="Tree-1", .before=.metric)
tree2 <- tree_rec2 %>% collect_metrics() %>% mutate(Model="Tree-2", .before=.metric)
tree3 <- tree_rec3 %>% collect_metrics() %>% mutate(Model="Tree-3", .before=.metric)
tree4 <- tree_rec4 %>% collect_metrics() %>% mutate(Model="Tree-4", .before=.metric)
tree5 <- tree_rec5 %>% collect_metrics() %>% mutate(Model="Tree-5", .before=.metric)
tree6 <- tree_rec6 %>% collect_metrics() %>% mutate(Model="Tree-6", .before=.metric)

tree_Comp <- rbind(tree1, tree2, tree3, tree4, tree5, tree6) %>% 
  dplyr::select(Model, .metric, mean) %>% 
  pivot_wider(names_from = .metric,
              values_from = mean)
tree_Comp
```
Tree-5

### Random Forest
```{r}
cores <- detectCores()

rf_mod <- 
  rand_forest(mtry = tune(), min_n = tune(), trees = 1000) %>% 
  set_engine("ranger", num.threads = cores) %>% 
  set_mode("classification")



rf_res <- rf_mod %>% 
  tune_grid(rec1,
            resamples = train_cv5,
            grid = 10,
            control = control_grid(save_pred = TRUE),
            metrics = metric_set(accuracy, roc_auc, recall, precision))
  
tuning_metrics2 <- rf_res %>% collect_metrics()

tuning_metrics2 %>% 
  filter(.metric == "accuracy") %>% 
  slice_max(mean)
```

rec1 - 58.64
rec4 - 58.09
rec2 - 58.04
rec3 - 58.04
rec5 - 58.02
rec6 - 58.61

```{r}
cores <- detectCores()
rf_mod <- 
  rand_forest(mtry = 15, min_n = 36, trees = 1000) %>% 
  set_engine("ranger", num.threads = cores) %>% 
  set_mode("classification")

rf_rec1 <- rf_mod %>% 
  fit_resamples(rec1, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
rf_rec2 <- rf_mod %>% 
  fit_resamples(rec2, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
rf_rec3 <- rf_mod %>% 
  fit_resamples(rec3, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
rf_rec4 <- rf_mod %>% 
  fit_resamples(rec4, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
rf_rec5 <- rf_mod %>% 
  fit_resamples(rec5, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
rf_rec6 <- rf_mod %>% 
  fit_resamples(rec6, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
```

```{r}
rf1 <- rf_rec1 %>% collect_metrics() %>% mutate(Model="RF-1", .before=.metric)
rf2 <- rf_rec2 %>% collect_metrics() %>% mutate(Model="RF-2", .before=.metric)
rf3 <- rf_rec3 %>% collect_metrics() %>% mutate(Model="RF-3", .before=.metric)
rf4 <- rf_rec4 %>% collect_metrics() %>% mutate(Model="RF-4", .before=.metric)
rf5 <- rf_rec5 %>% collect_metrics() %>% mutate(Model="RF-5", .before=.metric)
rf6 <- rf_rec6 %>% collect_metrics() %>% mutate(Model="RF-6", .before=.metric)

tree_Comp <- rbind(rf1, rf2, rf3, rf4, rf5, rf6) %>% 
  dplyr::select(Model, .metric, mean) %>% 
  pivot_wider(names_from = .metric,
              values_from = mean)
tree_Comp
```


### Neural Network

```{r}
nn_mod <- mlp(
  hidden_units = 12,
  penalty = 1,
  epochs = 100,
  activation = "linear") %>%
  set_engine("nnet") %>%
  set_mode("classification")

nn_rec1 <- nn_mod %>% 
  fit_resamples(rec1, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
nn_rec2 <- nn_mod %>% 
  fit_resamples(rec2, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
nn_rec3 <- nn_mod %>% 
  fit_resamples(rec3, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
nn_rec4 <- nn_mod %>% 
  fit_resamples(rec4, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
nn_rec5 <- nn_mod %>% 
  fit_resamples(rec5, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 
nn_rec6 <- nn_mod %>% 
  fit_resamples(rec6, 
                resamples = train_cv5, 
                metrics = metric_set(accuracy, roc_auc, precision, recall),
                control = control_resamples(save_pred = TRUE)) 

nn1 <- nn_rec1 %>% collect_metrics() %>% mutate(Model="NN-1", .before=.metric)
nn2 <- nn_rec2 %>% collect_metrics() %>% mutate(Model="NN-2", .before=.metric)
nn3 <- nn_rec3 %>% collect_metrics() %>% mutate(Model="NN-3", .before=.metric)
nn4 <- nn_rec4 %>% collect_metrics() %>% mutate(Model="NN-4", .before=.metric)
nn5 <- nn_rec5 %>% collect_metrics() %>% mutate(Model="NN-5", .before=.metric)
nn6 <- nn_rec6 %>% collect_metrics() %>% mutate(Model="NN-6", .before=.metric)

nn_Comp <- rbind(nn1, nn2, nn3, nn4, nn5, nn6) %>% 
  dplyr::select(Model, .metric, mean) %>% 
  pivot_wider(names_from = .metric,
              values_from = mean)
nn_Comp
```


```{r}
nn_grid <- grid_regular(
  hidden_units(c(2, 12)),
  penalty(c(-5, 0)),
  levels = 3
)

nn_mod_tune <- mlp(
  hidden_units = tune(),
  penalty = tune(),
  epochs = 100,
  activation = "linear") %>%
  set_engine("nnet") %>%
  set_mode("classification")

nn_wflow_tune <- workflow() %>%
  add_recipe(rec4) %>%
  add_model(nn_mod_tune)

nn_grid_search <-
  tune_grid(
    nn_wflow_tune,
    resamples = train_cv5,
    grid = nn_grid
  )

tuning_metrics <- nn_grid_search %>%
  collect_metrics()
tuning_metrics %>% 
  filter(.metric == "accuracy") %>% 
  slice_max(mean)
```



# Comparing all Classification Models 
```{r}
Model_Comp <- rbind(knn4, knn5, lda1, lda4, qda5, qda6, svm1, svm4, tree5, rf2, rf6, nn3, nn4) %>% 
  dplyr::select(Model, .metric, mean) %>% 
  pivot_wider(names_from = .metric,
              values_from = mean)
Model_Comp
```



# Predictions 
```{r}
test <- read.csv("CAH-201803-test.csv")

test <- test %>% 
  mutate(
    Q1 = factor(Q1),
    Q4 = factor(Q4),
    Q5 = factor(Q5),
    Q6 = factor(Q6),
    Q7 = factor(Q7),
    Q8 = factor(Q8),
    Q9 = factor(Q9),
    Q10 = factor(Q10),
    Q11 = factor(Q11),
    Q12 = factor(Q12),
    Q13 = factor(Q13),
    Q14 = factor(Q14),
    Q15 = factor(Q15),
    Q16 = factor(Q16),
    Q17 = factor(Q17),
    Q18 = factor(Q18)
  )
summary(test)
```

```{r}
rec4 <- recipe(political_affiliation ~ Q2 + Q4 + Q6 + Q10 + Q15 + Q17 + Q18, data = train)

knn_mod <- nearest_neighbor(neighbors = 35) %>%
  set_engine("kknn") %>%
  set_mode("classification")

knn_wflow <- workflow() %>%
  add_model(knn_mod) %>%
  add_recipe(rec4) 

knn_final <- knn_wflow %>% fit(train)
```



```{r}
final_predictions <- data.frame(
    id_num  = test$id_num,
    political_affiliation_predicted = predict(knn_final, test)$.pred_class
)
```

```{r}
final_predictions %>% write_csv("NickBias_FinalPredictions.csv")
```

